When does vapor pressure deficit drive or reduce evapotranspiration?

### 2017-09-27 doc/paper/vpd_et_paper.tex
going to make a coffe and think about fig 5

Before diving into calcualted values of $\frac{\partial \; ET}{\partial \; D}$, it is useful to consider the functional form of Equation \ref{d_et}. There are three terms: a scaling term for the full expression we will call Term 1 ($\frac{g_a \; P}{T(\Delta + \gamma)}$), a relatively constant offset we will call Term 2 ($\frac{c_p}{R_{air}}$), and a variable term we will call Term 3 ($- \frac{\gamma c_s }{\text{LAI }1.6 \; R\; \text{ uWUE }} \left( \frac{2 g_1 + \sqrt{D}}{2 (g_1 + \sqrt{D})^2}\right)$). All variables are constant, so the relative magnitude between Term 2 and Term 3 will determine the sign of the derivative, while Term 1 will scale the expression larger or smaller.

In Term 1, $\frac{P}{T} \propto \rho$, so this should vary little relative to $g_a$ and $\Delta$.  $\gamma$ should also be relatively constant, So the scaling term, Term 1, should be primarily a function of $g_a$ and temperature (though the function $\Delta$). Figure \ref{scale_vary} shows how the magnitude of the scaling varies with $T$ and $g_a$.

\begin{figure}[h]
\centering
\includegraphics[width=20pc]{./fig04.pdf}
\caption{Variability of Term 1 for each PFT. Each colored line correspondes to a different aerodynamic resistance.}
\label{lai_vpd_fig}
\end{figure}

>>>>

Before diving into calcualted values of $\frac{\partial \; ET}{\partial \; D}$, it is useful to consider the functional form of Equation \ref{d_et}. There are three terms: a scaling term for the full expression we will call Term 1 ($\frac{g_a \; P}{T(\Delta + \gamma)}$), a relatively constant offset we will call Term 2 ($\frac{c_p}{R_{air}}$), and a variable term we will call Term 3 ($\frac{\gamma c_s }{\text{LAI }1.6 \; R\; \text{ uWUE }} \left( \frac{2 g_1 + \sqrt{D}}{2 (g_1 + \sqrt{D})^2}\right)$). All variables are constant, so the relative magnitude between Term 2 and Term 3 will determine the sign of the derivative, while Term 1 will scale the expression larger or smaller.

In Term 1, $\frac{P}{T} \propto \rho$, so this should vary little relative to $g_a$ and $\Delta$.  $\gamma$ should also be relatively constant, So the scaling term, Term 1, should be primarily a function of $g_a$ and temperature (through the function $\Delta$). While temperature range may vary for PFT, the fucntional form of $\Delta$ will be the same. $g_a$ will vary strongly with PFT due to the importance of surface roughness. However, the coeffiecent of variability for $g_a$ is relatively constant across PFT. So, the influence of $g_a$ on the relative (to the mean) variability of Term 1 is approximately similiar across PFT.

Figure \ref{scale_vary}A shows Term 1 normalized by mean $g_a$ (calcualted for each plant functional type), and confirms that much of the relative variability of Term 1 is contained in the $g_a$ term's relative variability. Additionally, the impact of $T$ on the relative variability increases with increasing $g_a$.

While the relative variability of Term 1 is similiar across PFT, the absolute value of Term 1 varies strongly across PFT. Figure \ref{scale_vary}B shows Term 1 evaluated with the mean $g_a$ for each PFT, and at the range of observed temperatures for each PFT. As expected, for the tree PFTs, the Term 1 is much larger and the temperature dependence is much stronger. Additionally, because std$(g_a) \propto \overline{g_a}$, the spread of Term 1 due to $g_a$ variability will be larger, although this is not shown for simplicity.

\begin{figure}[h]
\centering
\includegraphics[width=20pc]{./fig04.pdf}
\caption{Primary sources of variability for Term 1. A) Term 1 normalized by mean $g_a$ for each PFT. B) Term 1 evaluated at mean $g_a$ for each PFT. Temperature range is 5-95th percentile for each PFT. Additionally, stars denote the location of the 25th, 50th, and 75th percentiles.}
\label{scale_vary}
\end{figure}
